---
title: "My awesome guide"
author: "Ford Prefect"
output: html_document
---

# Title
## Section
### Sub-section
#### Sub-sub section
##### Sub-sub-sub section

Blah blah blah... world-changing science...

## Introduction

This ***awesome*** well-written guide uses the **tidyverse** package along with the *SAFI*
dataset, which has columns that include:

- village
  + name of village
- interview_date
  + date of interview
    * ISO standard
- no_members
- years_liv
- respondent_wall_type
- rooms

This is a list of my favourite variables

1. interview_date
2. village
3. rooms
4. no_members

```{r setup, eval=FALSE, echo=FALSE}
library(tidyverse)
library(here)
interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL")
```

## Materials and methods

I did some stuff.

## Results

Here is a table.

```{r echo=FALSE, message=FALSE}
interviews %>% 
  filter(!is.na(memb_assoc)) %>% 
  group_by(village, memb_assoc) %>% 
  summarise(mean_no_membrs = mean(no_membrs)) %>% 
  knitr::kable(
    caption = "This is the aforementioned table.",
    col.names = c("Village", "Member Association", "Mean Number of Members")
  )
```




