---
title: "My awesome guide"
author: "Ford Prefect"
output: html_document
---

# Title
## Section
### Sub-section
#### Sub-sub section
##### Sub-sub-sub section

Blah blah blah... world-changing science...

## Introduction

This ***awesome*** well-written guide uses the **tidyverse** package along with the *SAFI*
dataset, which has columns that include:

- village
  + name of village
- interview_date
  + date of interview
    * ISO standard
- no_members
- years_liv
- respondent_wall_type
- rooms

This is a list of my favourite variables

1. interview_date
2. village
3. rooms
4. no_members

```{r setup, include=FALSE}
library(tidyverse)
library(here)
interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL")
interviews_plotting <- read_csv(here("data_output/interviews_plotting.csv"))
```

## Materials and methods

I did some stuff.

## Results

Here is a table.

```{r echo=FALSE, message=FALSE}
interviews %>% 
  filter(!is.na(memb_assoc)) %>% 
  group_by(village, memb_assoc) %>% 
  summarise(mean_no_membrs = mean(no_membrs)) %>% 
  knitr::kable(
    caption = "This is the aforementioned table.",
    col.names = c("Village", "Member Association", "Mean Number of Members")
  )
```

```{r}
mean_household <- interviews %>%
  group_by(village) %>% 
  summarise(mean_no_membrs = mean(no_membrs))

mean_chirodzo <- mean_household %>% 
  filter(village == "Chirodzo")
```

The average household size in the village of Chirodzo is `r mean_chirodzo$mean_no_membrs`.

### Plots

Here are some plots.

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items)) +
    geom_point(alpha = 0.2) # specify level of opacity/transparency for each point
```


That is not ideal for integers...

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items)) +
    geom_jitter(
      colour = "blue",
      alpha = 0.3,
      width = 0.2, # specify level of random noise on x-axis
      height = 0.2 # specify level of random noise on y-axis
    )
```

```{r}
interviews_plotting %>%
  ggplot(aes(x = no_membrs, y = number_items, colour = village)) +
    geom_count()
```

Exercise 2

🕰 6 mins

Create a new code chunk with the label rooms-village-scatter.

Create a scatter plot of rooms by village with the respondant_wall_type showing in different colours.

Does this seem like a good way to display the relationship between these variables?

What other kinds of plots might you use to show this type of data?






