---
title: "My awesome guide"
author: "Ford Prefect"
output: html_document
---

# Title
## Section
### Sub-section
#### Sub-sub section
##### Sub-sub-sub section

Blah blah blah... world-changing science...

## Introduction

This ***awesome*** well-written guide uses the **tidyverse** package along with the *SAFI*
dataset, which has columns that include:

- village
  + name of village
- interview_date
  + date of interview
    * ISO standard
- no_members
- years_liv
- respondent_wall_type
- rooms

This is a list of my favourite variables

1. interview_date
2. village
3. rooms
4. no_members

```{r setup, include=FALSE}
library(tidyverse)
library(here)
interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL")
interviews_plotting <- read_csv(here("data_output/interviews_plotting.csv"))
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = here("fig_output/")
  )
```

## Materials and methods

I did some stuff.

## Results

Here is a table.

```{r echo=TRUE, message=FALSE}
interviews %>% 
  filter(!is.na(memb_assoc)) %>% 
  group_by(village, memb_assoc) %>% 
  summarise(mean_no_membrs = mean(no_membrs)) %>% 
  knitr::kable(
    caption = "This is the aforementioned table.",
    col.names = c("Village", "Member Association", "Mean Number of Members")
  )
```

```{r}
mean_household <- interviews %>%
  group_by(village) %>% 
  summarise(mean_no_membrs = mean(no_membrs))

mean_chirodzo <- mean_household %>% 
  filter(village == "Chirodzo")
```

The average household size in the village of Chirodzo is `r mean_chirodzo$mean_no_membrs`.

### Plots

Here are some plots.

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items)) +
    geom_point(alpha = 0.2) # specify level of opacity/transparency for each point
```


That is not ideal for integers...

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items)) +
    geom_jitter(
      colour = "blue",
      alpha = 0.3,
      width = 0.2, # specify level of random noise on x-axis
      height = 0.2 # specify level of random noise on y-axis
    )
```

```{r}
interviews_plotting %>%
  ggplot(aes(x = no_membrs, y = number_items, colour = village)) +
    geom_count()
```
<!-- comment 
Exercise 2

🕰 6 mins

Create a new code chunk with the label rooms-village-scatter.

Create a scatter plot of rooms by village with the respondant_wall_type showing in different colours.

Does this seem like a good way to display the relationship between these variables?

What other kinds of plots might you use to show this type of data? -->

Enough with the mediocre plots. Here's one awesome plot to rule them all.

```{r}
interviews_plotting %>% 
  ggplot(aes(x = respondent_wall_type, fill = village)) +
    geom_bar(position = "dodge")
```

```{r}
percent_wall_type <- interviews_plotting %>% 
  filter(respondent_wall_type != "cement") %>%  # get rid of cement observations
  count(village, respondent_wall_type) %>% 
  group_by(village) %>% 
  mutate(percent = (n / sum(n)) * 100) %>% # calculate percentage of each wall type in a village
  ungroup() # ungroup for good measure!
```


```{r my-plot, fig.cap="This is my caption."}
percent_wall_type %>% 
  ggplot(aes(x = respondent_wall_type, y = percent, fill = respondent_wall_type)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(
      title = "Proportion of wall type by village",
      fill = "Type of Wall in Home",
      x = "Village",
      y = "Percent"
    ) +
  facet_wrap(~ village) +
  theme_bw() +
  theme(
    panel.grid.major.x = element_blank(),
    legend.position = "none"
  )

ggsave("fig_output/my_plot.png")
```



